### 2016-03-22 paper.tex
Add introduction paragraph about narratology and ludology

@@

\textit{In which we make and justify some conclusions, and point toward
 other areas that this work could be extended}

>>>>

The role and meaning of narrative in games is a perennial topic
of discussion among game design theorists.
We hope to position this work not as one of ludology or narratology,
but more pragmatically as part of a systematic investigation of how
systems and stories interact to produce learning outcomes.

@@
